Kimbee: A Speech Therapy Application For Children

### 2015-03-09 Paper/paper.tex
fixed

We have developed an application named {\em Kimbee} that aims to help the process of speech therapy in young children. Speech therapies are often expensive for schools and parents to maintain, especially with younger children who require more time than others. Our application does not replace the speech therapist, rather it supplements the therapy. Instead of being limited to short sessions, therapists can use {\em Kimbee} to have their students work at home as well as in the classroom. The therapist can then monitor the child's progress through our application and use this newly gained information to further tailor the therapy to individual students. This will save both time and money for school districts and parents who are paying for their child's therapy.

@@

\subsubsection{Gameplay}

The game has a simple interface that is easy for a child to navigate, see Figure \ref{fig:user}. Children simply tap the screen to make their character, a bee, move along the y-axis of the screen. Collecting honey causes their score to increase and colliding with an enemy bee causes the game to end. Interleaved with the enemy bees and honey pots is a special honey pot that will grant a significant amount of honey if a challenge is completed. This challenge consists of having the child speak into the microphone of his or her device and say a designated word or phrase that appears on the screen. The difficulty of the text increases over time to simulate the treatment that the child would receive during a therapist session \cite{Rosenbek:Treatment}. If the system succeeds in verifying that the child spoke the text correctly, then the currency is added to the child's score. If the child fails to correctly pronounce the phrase or if the system fails to recognize the audio, then the child is asked to try again in order to continue. To avoid discouraging the child, {\em Kimbee} will say a positive statement asking him or her to try again to continue playing the game \cite{Kreider:Intro}.

@@

[User Flow Therapist Portal Here]

@@

\subsubsection{Speech Processing Component}
The {\em Speech Processing Component} of the Kimbee system handles all audio processing and speech related requests from the {\em Phaser Game Implementation}. Requests are made through an API Singleton that is constructed on game load. These include requests such as getting the next practice word for a particular speech problem, setting which speech problem the child is working on, and harvesting microphone data. Harvesting and processing microphone levels is a multithreaded process implemented with HTML5 Web Workers. When the application is started and the API Singleton is constructed, audio stream {\em consumers} are created to process future audio streams in seperate threads. Once a microphone ``Start'' request is made from the {\em Phaser Game Implementation}, the following steps are executed:
\begin{enumerate}
  \item
    Web Workers are initalized to start processing the audio stream in parallel.
  \item
    Each stream buffer is processed by each Web Worker in parallel as the microphone streams raw Left-Right buffers.
  \item
    Once a microphone ``Stop'' request is made from the {\em Phaser Game Implementation}, the consumers are queried for final results of their processing.
\end{enumerate}
Currently there are two {\em consumers}: an {\em AudioStorageConsumer}, and a {\em RecognizerConsumer}. The {\em AudioStorageConsumer} simply stores the raw microphone levels, while the {\em RecognizerConsumer} communicates with the {\em CMU Sphinx Component} to iterate a best guess for the correctness of the child's speech.

\subsubsection{CMU Sphinx Component}

@@

[High Level Overview of Therapist Portal (tech)]

>>>>

We have developed an application named {\em Kimbee} that aims to help improve the process of speech therapy in young children. Speech therapies are often expensive for schools and parents to maintain, especially with younger children who require more time than others. Our application does not replace the speech therapist, rather it supplements the therapy. Instead of being limited to short sessions, therapists can use {\em Kimbee} to have their students work at home as well as in the classroom. The therapist can then monitor the child's progress through our application and use this newly gained information to further tailor the therapy to individual students. This will save both time and money for school districts and parents who are paying for their child's therapy.

@@

\subsubsection{Gameplay\label{sec:gameplay_flow}}

The game has a simple interface that is easy for a child to navigate, see Figure \ref{fig:user}. Children simply tap the screen to make their character, a bee, move along the y-axis of the screen. Collecting honey causes their score to increase and colliding with an enemy bee causes the game to end. Interleaved with the enemy bees and honey pots is a special honey pot that will grant a significant amount of honey if a challenge is completed. This challenge consists of having the child speak into the microphone of his or her device and say a designated word or phrase that appears on the screen.

The difficulty of the text increases over time to simulate the treatment that the child would receive during a therapist session \cite{Rosenbek:Treatment}. If the system succeeds in verifying that the child spoke the text correctly, then the currency is added to the child's score. If the child fails to correctly pronounce the phrase or if the system fails to recognize the audio, then the child is asked to try again in order to continue. To avoid discouraging the child, {\em Kimbee} will say a positive statement asking him or her to try again to continue playing the game.

@@

The therapist is responsible for tailoring lesson plans for each session with his or her students. Currently, this involves taking detailed notes during every session to document and track the progress of each student over time \cite{Kreider:Intro}. The goal of the Therapist Portal is to improve and simplify this process to increase the quality of treatment given to the student. As described in section \ref{sec:gameplay_flow}, every recording that each child produces will be sent to the central server. These recordings are then sent to Therapist Portal and listed for every student under the therapist. Additional data is sent down with each recording to help the therapist focus on words that the student had trouble speaking. For example, whether the child said the word or phrase correctly is included with the recording allowing the therapist to filter the recordings.

After listening to all of the recordings that the child produced for homework, the therapist will have a good idea for where the student currently is in terms of progress.

@@

\subsubsection{Speech Processing}
The {\em Speech Processing} of the Kimbee system handles all audio processing and speech related requests from the {\em Phaser Game Implementation}. Requests are made through an API Singleton that is constructed on game load. These include requests such as getting the next practice word for a particular speech problem, setting which speech problem the child is working on, and harvesting microphone data. Harvesting and processing microphone levels is a multithreaded process implemented with HTML5 Web Workers. When the application is started and the API Singleton is constructed, audio stream {\em consumers} are created to process future audio streams in seperate threads. Once a microphone ``Start'' request is made from the {\em Phaser Game Implementation}, the following steps are executed:
\begin{enumerate}
  \item
    Web Workers are initalized to start processing the audio stream in parallel.
  \item
    Each stream buffer is processed by each Web Worker in parallel as the microphone streams raw Left-Right buffers.
  \item
    Once a microphone ``Stop'' request is made from the {\em Phaser Game Implementation}, the consumers are queried for final results of their processing.
\end{enumerate}
Currently there are two {\em consumers}: an {\em AudioStorageConsumer}, and a {\em RecognizerConsumer}. The {\em AudioStorageConsumer} simply stores the raw microphone levels, while the {\em RecognizerConsumer} communicates with the {\em CMU Sphinx} to iterate a best guess for the correctness of the child's speech.

\subsubsection{CMU Sphinx}
CMU Sphinx\cite{CMU:Sphinx} is a speech processing library. There is a JavaScript port that allows audio recognition in the browser. Our {\em Speech Processing} component utilizes this JavaScript port to do audio recognition in the browser without server assistance. To deduce correct child speech we utilize this library creating target word and invalid word pairs. For example, when targeting `R' sounds, we can use CMU Sphinx to recognize the target word `Rabbit' or a invalid word `Wabbit.' With a large dictionary of words this has been effective in distinguishing replacements caused by speech disorders.

\subsubsection{Server Application Programming Interface}
The {\em Server Application Programming Interface} is what connects the Kimbee system to our central recording server. Once audio is processed by the {\em Speech Processing}, it is sent off via POST request in raw microphone form to the central server if a internet connection is present. A unique identifier is computed and stored by the Kimbee System that will uniquely identify recordings in the central server as belonging to a particular child's device. This unique identifier is accessible via the Options Screen in the {\em Phaser Game Implementation}.

@@

\subsubsection{Connection to Child Audio}

\subsubsection{Playing of Audio}

\subsubsection{Caching System}
